01 - Simulate data

### 2023-11-27 scripts/01_sim_data.qmd
fix wrong subj int and slo
edit dat2

```{r}

```

>>>>

```{r}
set.seed(my_seed)

subjs <- 60
timep <- 9
reps <- 6

dat2_grid <- expand_grid(
  subj = 1:subjs,
  group = c("es", "es_0", "es_1"),
  vowel = c("i", "u", "a"),
  rep = 1:reps
)

subj_int <- rnorm(subjs * 3, 0, 0.15)
subj_slo <- rnorm(subjs * 3, 0, 0.25)

dat2 <- tibble()

for (rown in 1:nrow(dat2_grid)) {
  # Get current row, group and vowel
  this_row <- dat2_grid[rown,]
  this_subj <- this_row$subj
  this_group <- this_row$group
  this_vowel <- this_row$vowel
  this_int <- rnorm(1, 0, 0.2)
  this_slo <- rnorm(1, 0, 0.2)

  # Calculate EUD trajectory
  if (this_group == "es") {
    if (this_vowel == "i") {
      this_eud <- rep(2.25 + subj_int[this_subj] + this_int, 9)
    } else if (this_vowel == "u") {
      this_eud <- rep(2 + subj_int[this_subj] + this_int, 9)
    } else if (this_vowel == "a") {
      this_eud <- rep(1.5 + subj_int[this_subj] + this_int, 9)
    }

  } else if (this_group == "es_0") {
    if (this_vowel == "i") {
      this_eud <- 2 + (-0.3 + subj_int[this_subj] + this_int - 2) /
        (1 + (1:timep/2)^(2.5 + (subj_slo[this_subj] + this_slo) * 2))
    } else if (this_vowel == "u") {
      this_eud <- 1.6 + (-4 + subj_int[this_subj] + this_int - 1.6) /
        (1 + (1:timep/0.5)^(1.5 + subj_slo[this_subj]  + this_slo))
    } else if (this_vowel == "a") {
      this_eud <- rep(0 + subj_int[this_subj] + this_int, 9)
    }

  } else if (this_group == "es_1") {
    if (this_vowel == "i") {
      this_eud <- 2 + (0.9 + subj_int[this_subj] + this_int - 2) /
        (1 + (1:timep/2)^(2.5 + subj_slo[this_subj] + this_slo))
    } else if (this_vowel == "u") {
      this_eud <- 1.5 + (1 + subj_int[this_subj] + this_int - 1.5) /
        (1 + (1:timep/0.5)^(2.5 + subj_slo[this_subj] + this_slo))
    } else if (this_vowel == "a") {
      this_eud <- rep(1.25 + subj_int[this_subj] + this_int, 9)
    }
  }

  # Add eud to dat2
  this_row$eud <- list(this_eud)
  this_trial <- unnest(this_row, eud)
  this_trial$timep <- 1:timep
  dat2 <- bind_rows(dat2, this_trial)
}

dat2 <- dat2 %>%
  mutate(
    id = paste(group, subj, rep, sep = ".")
  )
```

```{r}
dat2 %>%
  ggplot(aes(timep, eud, group = id, colour = group)) +
  geom_path(alpha = 0.15, linewidth = 1) +
  facet_grid(cols = vars(vowel), rows = vars(group))
```

```{r}
dat2 %>%
  ggplot(aes(timep, eud, colour = group)) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 3)) +
  facet_grid(cols = vars(vowel), rows = vars(group))
```

```{r}
dat2 %>%
  filter(subj == 1, group == "es_0") %>%
  ggplot(aes(timep, eud, group = id, colour = as.factor(rep))) +
  geom_path() +
  facet_grid(cols = vars(vowel))
```
